---
title: 'Annual Report for Linear Analysis'
output: html_document
params:
  file: 
   input: file
   label: "Choose RDS"
   value: ""
   multiple: FALSE
   buttonLabel: "Browse to analysis output..."
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(knitr)
ps <- readRDS(params$file)
```


## Linear Equation Report


This report summarizes an analysis done by `r ps$userName` for Shire Data Science in `r format(as.POSIXct(ps$timestamp), '%Y')`.   `r ps$userName` collected `r  ps$"mod1-nPts"` datapoints.  The data are shown below.



```{r, fig.cap= paste0("Figure 1.  Data collected by ", ps$userName)}
# browser()
x_data <- ps$returns$data1$x
y_data <- ps$returns$data2$y_perturbed
y_pred <- predict(lm(y_data ~ poly(x_data, ps$returns$data3$degree)))[order(x_data)]
gg <- ggplot(data.frame(x = x_data, y = y_data), aes(x, y)) + geom_point() + geom_line(
          data = data.frame(
            x = x_data[order(x_data)],
            y = y_pred
          ), 
          color = "red"
        )         + xlim(range(x_data)) + ylim(range(c(y_data, y_pred)))

# gg <- ps$returns$data3$g
plot(gg)
```
`r ps$userName` was able to fit a polynomial of degree `r ps$returns$data3$degree` to the data, with the following coefficients:

```{r}
model_coeffs <- ps$returns$data3$coeff
rownames(model_coeffs) <- c("Intercept", "Coefficient 1", "Coefficient 2")

kable(model_coeffs, caption = "Linear coefficients")
```

We look forward to next year's analysis.

Respectfully submitted,

Gandalf



